What do they see? Testing perceptual accuracy in a U.S. general population survey using stacked bar charts

### 2023-10-26 revisions-round1/response-to-reviewers.qmd

-   **I believe the figures are fairly clear (per Reviewer 1's comment), but the authors might also be inclined to be more selective with what is shown in Figures 3, 6-8, and maybe move some of the others to an appendix.**

-   Can the authors comment further on modeling assumptions, particularly in relation to presenting all participants with the unaligned plot first followed by the aligned plot second (as opposed to randomizing this)? For instance, perhaps some participants notice that the plots are the same, with just the bars stacked in a different order, and their response to the second task is biased to be equivalent to that of the first task. This seems like it would be more of a problem if the plots were presented in the reverse order, but I'm curious if the authors looked into this.

    -   *We acknowledge that this is a limitation. There is a chance that someone recognizes they are completing the same task with the same bars when we present the aligned task before the unaligned task; we made the assumption that the chance of recognizing the tasks is lower when seeing unaligned prior to aligned. Participants are not able to return to the prior question once they move on to the second question, which does make it more difficult for participants to compare the tasks to one another. We also added the following text in the section describing alignment: "Participants first saw the chart with the unaligned comparison, followed by the chart with the aligned comparison, but could not return to the first comparison after completing it. While there is some risk of participants recognizing the subsequent tasks to be the same value comparisons, the unaligned (harder) task was shown first to reduce the likelihood of participants carrying over an answer from the aligned (easier) task."*

-   Is there a reason why the meaning/values of i from 1 to 3 are reversed between the two models specified in Equations 4 and 7?

    -   *The order in 4 is the correct one, and was actually the parameterization used for both models and shown in both corresponding tables. We have fixed the description for Equation 7 to reflect this.*

### 2023-10-27 revisions-round1/response-to-reviewers.qmd

    -   **Figure 1, the text within the visualisation are too small to see. Perhaps lay it out as a 3 x 2 instead?**
            - HH: *Figure 1 was not meant to have readable text within the stimuli visualizations but only give an overview of the different stimuli and the testing situations. We have increased the font size for the overview, expanded the discussion of the figure to reflect its purpose and added image (a) to the supplement in a larger format.* **create supplement and add stimulus**

    -   page 8, first paragraph: "\$ 2\$" is a typo?
        -   *This was a typesetting error and has been resolved in the source code.*

    -   Table 1, effective sample size adds up to 1520.3 but the total says 1520.8? 
        -   *What is shown is the effective sample size of the combined survey rounds, not the total of each round's effective sample size. The fact that these numbers are close is due to similar weighting strategies being used in each of the individual rounds. We have now renamed the line "Combined Rounds" to reduce confusion.*

    -   Figure 3: I take it that the American Community Survey 2021 is considered the Census estimates? I think it makes more sense to swap the bar and point so that the bar is the Census estimate. This way you can use the errorbar plot. The margin of error around a barplot is reminiscent of a dynamite plot, which I don't think is well thought of in the community (at least not me). I think you can also color the bars to indicate whether your survey estimate covers the census estimate so it is easier to see which one covers it or not. In this plot, you've facetted by the stimulus type but I think it makes sense to facet by the category level (the comparison of distribution is done with the census estimate directly, and I think the interest is to compare the distribution across stimulus so you want the primary factor of interest to compare to be close in proximity). Within a category level, the census estimate is constant across stimulus so you could substitute is with a horizontal line (instead of a bar or point) as well.
        -   *We have changed the format of this figure to address these concerns, using a dot plot with error bars to represent the uncertainty.*

### 2023-10-27 SDSS-2023/testing-charts-accuracy.qmd
eqns 4 and 7
demographics

rounds_col <- RColorBrewer::brewer.pal(name="Accent", n=8)[c(1,3,5)]
#[1] "#7FC97F" "#BEAED4" "#FDC086" "#FFFF99" "#386CB0" "#F0027F" "#BF5B17" "#666666"
gender <- acs_gender %>%
  ggplot(aes(x = gender)) +
  geom_errorbar(aes(ymin = percent-moe_percent, ymax=percent+moe_percent, colour="ACS estimate")) +
#  geom_point(aes(y = percent)) +
  geom_point(
    size=3,
    aes(x = sex, y = value, colour=chart),
    position = position_dodge(width = 0.5),
    data = omni_gender %>% filter(group=="mean")
  ) +
  ylim(c(0, NA)) +
  geom_linerange(
    aes(
      x = sex,
      ymin = low,
      ymax=high,
      colour=chart
    ),
    linewidth = 1, 
    position = position_dodge(width = 0.5),
    data = omni_gender %>% pivot_wider(names_from=group, values_from=value),
    show.legend = FALSE
  ) +
  ylab("Percent") + 
  ggtitle("Gender") +
#  theme(axis.text.x = element_text(angle=0, vjust = 0.5)) +
  xlab("") +
#  theme(legend.position ="none") +
  scale_linetype_manual(values=c(2,2,1)) +
  scale_color_manual(values=c("grey20", rounds_col))

@@

@@

@@

```{r}
#| label: fig-certainty
#| out-width: 100%
#| fig-cap: "Certainty by task, chart design, and correctness. Correct answers in the unaligned task have the lowest certainty scores associated with them. Incorrect responses on the unaligned task show a significant boost in certainty in the vertical stacked bar. For horizontal stacked bars the difference between aligned and unaligned charts matters significantly. Error bars around the points show estimated scores (on a scale of 1 to 5) with corresponding 95% CI. The letters underneath the bars indicate significance at 5%. The scores for two bars are significantly different if they do not share a letter. "
#| fig-width: 10
#| fig-height: 4.25

@@

Let $Y_k$ be the response of participant $k$, on a scale from 1 = 'wrong', 2 = 'they are the same' to 3 = 'correct'.
We use a generalized cumulative logistic regression, where $\mu_i$ are intercepts $1 \le i < 3$, $X_k$ are demographics of the $k$th participant (in form of the model matrix), and $\beta_{i}$ are the coefficients.

@@

```{r}
#| label: fig-demographics
#| fig-cap: "Response patterns by alignment and demographic levels. For aligned tiles, gender, age, and education are not significant factors. However, income levels do have a (small) effect. When income levels increase, the percentage of wrong answers decreases, while the percentage of correct answers increases slightly (significant at 5%). For the  more difficult task of comparing unaligned tiles, higher levels of education and higher levels of income are associated with a significant increase of panelists choosing a response of 'they are the same', resulting in significant decreases of both correct answers and wrong answers. "
#| fig-subcap: 
#|   - Comparisons of aligned tiles
#|   - Comparisons of unaligned tiles
#| fig-height: 4.5
#| fig-width: 10
#| layout-nrow: 2
#| out-width: 100%

>>>>

rounds_col <- RColorBrewer::brewer.pal(name="Accent", n=8)[c(1,3,5)]
#[1] "#7FC97F" "#BEAED4" "#FDC086" "#FFFF99" "#386CB0" "#F0027F" "#BF5B17" "#666666"
gender <- acs_gender %>%
  ggplot(aes(x = gender)) +
  geom_errorbar(aes(ymin = percent-moe_percent, ymax=percent+moe_percent, colour="ACS estimate")) +
#  geom_point(aes(y = percent)) +
  geom_point(
    size=3,
    aes(x = sex, y = value, colour=chart),
    position = position_dodge(width = 0.5),
    data = omni_gender %>% filter(group=="mean")
  ) +
  ylim(c(0, NA)) +
  geom_linerange(
    aes(
      x = sex,
      ymin = low,
      ymax=high,
      colour=chart
    ),
    linewidth = 1, 
    position = position_dodge(width = 0.5),
    data = omni_gender %>% pivot_wider(names_from=group, values_from=value),
    show.legend = FALSE
  ) +
  ylab("Percent") + 
  ggtitle("Gender") +
#  theme(axis.text.x = element_text(angle=0, vjust = 0.5)) +
  xlab("") +
  theme(legend.position ="none") +
  scale_linetype_manual(values=c(2,2,1)) +
  scale_color_manual(values=c("grey20", rounds_col))

@@

gender <- 
  gender +
  annotate("text", x = 0.83, y = 5, label="ACS estimate", hjust=0, 
           size = 5, colour = "grey20") +
  annotate("segment", x = 0.5, xend=0.7, y = 5,yend=5, 
           linewidth = 1, colour="grey20") +
  annotate("text", x = 0.83, y = 15, label="Horizontal design", hjust=0,
           size = 5, colour = "grey20") +
  annotate("segment", x = 0.8333, xend = 0.8333, y = 17, yend=40, 
           linewidth = 0.75, colour=rounds_col[1], linetype=2) +
  annotate("text", x = 1, y = 20, label="Horizontal wide", hjust=0,
           size = 5, colour = "grey20") +
  annotate("segment", x = 1, xend = 1, y = 22, yend=40, 
           linewidth = 0.75, colour=rounds_col[2], linetype=2) +
  annotate("text", x = 1.17, y = 25, label="Vertical design", hjust=0,
           size = 5, colour = "grey20") +
  annotate("segment", x = 1.166, xend = 1.166, y = 27, yend=40, 
           linewidth = 0.75, colour=rounds_col[3], linetype=2)

@@

```{r eval=FALSE, include=FALSE}
omni <- rbind(
omni_gender %>% rename(levels = sex) %>% 
  mutate(variable = "Gender"),
omni_age %>% rename(levels = age) %>% 
  mutate(variable = "Age groups"),
omni_income %>% rename(levels = income) %>% 
  mutate(variable = "Household income"),
omni_educ %>% rename(levels = educ) %>% 
  mutate(variable = "Education"))

acs <- rbind(
acs_age %>% rename(levels = age4) %>% mutate(variable = "Age groups") %>% 
  dplyr::select(variable, levels, percent2, moe_percent) %>% rename(percent = percent2),
acs_educ5 %>% rename(levels = educ5) %>% mutate(variable = "Education") %>% 
  dplyr::select(variable, levels, percent, moe_percent), 
acs_gender %>% rename(levels = gender) %>% mutate(variable = "Gender") %>% 
  dplyr::select(variable, levels, percent, moe_percent), 
acs_income %>% rename(levels = income4) %>% mutate(variable = "Household income") %>%
  dplyr::select(variable, levels, percent, moe_percent)
)

acs %>% 
  ggplot(aes(y = levels)) + 
  geom_errorbar(aes(xmin = percent-moe_percent, xmax = percent + moe_percent, colour = "ACS Est.")) +
  facet_grid(rows = vars(variable), space="free", scales = "free") +
  xlim(c(0,NA)) + ylab("") + xlab("Percent") +
  scale_color_manual(values=c("grey20", rounds_col)) +
  geom_linerange(
    aes(
      y = levels,
      xmin = low,
      xmax=high,
      colour=chart
    ),
    linewidth = 1, 
    position = position_dodge(width = 0.5),
    data = omni %>% pivot_wider(names_from=group, values_from=value),
    show.legend = FALSE
  )

@@

```{r}
#| label: fig-certainty
#| out-width: 95%
#| fig-cap: "Certainty by task, chart design, and correctness. Correct answers in the unaligned task have the lowest certainty scores associated with them. Incorrect responses on the unaligned task show a significant boost in certainty in the vertical stacked bar. For horizontal stacked bars the difference between aligned and unaligned charts matters significantly. Error bars around the points show estimated scores (on a scale of 1 to 5) with corresponding 95% CI. The letters underneath the bars indicate significance at 5%. The scores for two bars are significantly different if they do not share a letter. "
#| fig-width: 10
#| fig-height: 4.25

@@

Let $Y_k$ be the response of participant $k$, on a scale from 1 = 'correct', 2 = 'they are the same' to 3 = 'wrong'.

We use a generalized cumulative logistic regression, where $\mu_i$ are intercepts $1 \le i < 3$, $X_k$ are demographics of the $k$th participant (in form of the model matrix), and $\beta_{i}$ are the coefficients.

@@

```{r}
#| label: fig-demographics
#| fig-cap: "Response patterns by alignment and demographic levels. For aligned tiles, gender, age, and education are not significant factors. However, income levels do have a (small) effect. When income levels increase, the percentage of wrong answers decreases, while the percentage of correct answers increases slightly (significant at 5%). For the  more difficult task of comparing unaligned tiles, higher levels of education and higher levels of income are associated with a significant increase of panelists choosing a response of 'they are the same', resulting in significant decreases of both correct answers and wrong answers. "
#| fig-subcap: 
#|   - Comparisons of aligned tiles
#|   - Comparisons of unaligned tiles
#| fig-height: 4.5
#| fig-width: 10
#| layout-nrow: 2
#| out-width: 95%
